Internal Gravity Wave Breaking in White Dwarf Binaries

### 2019-11-05 writeups/Su_IGW_break.tex
stash, bunch of new plots again

% cp ../sims/agg.png plots;
% cp ../sims/2d_3_final/snapshots_lin_0_masked/f_amps.png plots/lin_amps.png;
% cp ../sims/2d_3_final/snapshots_lin_0_masked/fluxes.png plots/lin_fluxes.png;
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_amps.png plots/nl_f_amps.png;
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/fluxes.png plots/nl_fluxes.png;
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_refl.png plots/nl_f_refl.png;
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_ri.png plots/nl_f_ri.png;
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/front.png plots/nl_front.png;

@@

An equivalent estimate given by \citep{eliassen_palm_cite,sutherland0} is that
IGWs break when the wave-induced mean flow is equal to the horizontal phase
velocity
\begin{equation}
    \overline{U}(z) = \frac{\ev{u_{x}u_{z}}_x}{c_{g,z}} \sim
        \frac{\omega}{k_x},\label{eq:mean_flow}
\end{equation}
where $\bar{U}(z) \equiv \ev{u_x}_x$ is the mean flow of the fluid.
\autoref{eq:mean_flow} provides a leading-order estimate for $\bar{U}(z)$ which
may further evolve over time (see \autoref{ss:crit_layer}); for a general mean
flow, \autoref{eq:mean_flow} also defines the criterion for a \emph{critical
layer}. This wave-induced mean flow is analogous to Stokes' drift for surface
waves and can be derived by considering the propagation of $F$
(\autoref{eq:F_def}) into a medium at rest. Evaluating \autoref{eq:mean_flow} yields
agreement with \autoref{eq:nl}.

\subsection{Critical Layer Dynamics}\label{ss:crit_layer}

% critical layer does form
% previous studies of fluid interaction @ critical layer

The detailed onset of wave breaking has been laid out in a few key papers
\citep{drazin, klostermeyer, winters1994}, where instabilities transfer momentum
out of the IGW through daughter modes into the mean flow of the fluid. When
viscosity is sufficiently weak (see \autoref{ss:disp} for a discussion of this
assumption in WDs), a non-uniform shear flow and eventually a critical layer
develop. The further evolution of the critical layer with the incident IGW is
thought to be responsible for tidal synchronization in stellar binaries
\citep{zahn75,gn89} as well as terrestrial phenomena such as the quasi-biennial
oscillation \citep{lindzen_qbo}.

@@

Consider the horizontal momentum transfer at the critical layer. Any incident
horizontal momentum flux absorbed by the fluid must manifest as additional
horizontal momentum of the shear flow. Since the mean flow cannot exceed
$\overline{U}_c \equiv \omega/k_x$, the horizontal phase velocity of the
incident wave, the critical layer will instead propagate downward in response to
the incident momentum flux. The horizontal momentum of the shear flow satisfies
\begin{equation}
    \pd{}{t}\int\limits \overline{\rho}(z) \overline{U}(z, t)\;\mathrm{d}z
        - \Delta F = 0,
\end{equation}
where $\Delta F > 0$ is the absorbed horizontal momentum. Assuming
$\overline{U}(z > z_c) = \overline{U}_c, \overline{U}(z < z_c) = 0$, this
condition becomes
\begin{equation}
    \overline{\rho}(z_c) \overline{U}_c\rd{z_c}{t} = \Delta F.\label{eq:zc_anal}
\end{equation}
If $\Delta F$ is constant in time, $z_c(t)$ has analytical solution
\begin{equation}
    z_c(t) = -H\ln \frac{\overline{\rho}(t = 0)
        + t\frac{\Delta F}{\overline{U}_c H}}{\overline{\rho}_0}
        ,\label{eq:zc_sol}
\end{equation}
where $\overline{\rho}(t_0)$ is the density at the critical layer height at $t =
0$.

\section{Internal Gravity Waves: Weakly Forced Numerical
Simulations}\label{s:sim}

\subsection{Numerical Setup}\label{ss:numerics}

@@

@@

    \item $C$: In our linear simulations, we first choose $C$ forcing strength
        such that $\xi_z k_z \ll 1$ is satisfied everywhere in the simulation
        domain. This constrains $C$ by \autoref{eq:uz_lin}.

@@

We aim to damp waves that reach the edge of the simulation domain without
inducing nonphysical reflection. To do so, we replace material derivatives
in \autoref{se:nl_upsilon} with:
\begin{align}
    \md{}{t} &\to \md{}{t} + \Gamma(z)\Upsilon,\nonumber\\
    \Gamma(z) &= \frac{1}{2\tau}\s{2 + \tanh \frac{z - z_T}{\Delta z}
        + \tanh \frac{z_B - z}{\Delta z}},\label{eq:Gamma}
\end{align}
where $z_B = 0.05L_z, z_T = 0.95L_z$ are the boundaries of the damping zone.
This strongly damps perturbations below $z_B$ and above $z_T$ with damping time
$\tau$, negligibly affects dynamics between $z_B, z_T$ and has transition width
governed by $\Delta z$. We use $\Delta z = 0.025L_z$ and $\tau = 1/15N$. This
prescription is similar to \citep{lecoanet_damp} and has the advantage of being
smooth, important for spectral methods. Further details of our implementation of
the fluid equations in Dedalus are described in Appendix~\ref{se:strat_impl}.

\subsection{Simulation Results}\label{ss:lin_ns}

@@

The analytical theory also predicts that the horizontal momentmum flux $F(z, t)$
should be independent of $z$ between the forcing zone where it is generated and
the damping zone where it is dissipated (\autoref{eq:F_def}). We make may a
slightly more accurate estimate of the flux carried in the IGW by directly
substituting $\bm{u}_{al}$ into \autoref{eq:F_def}. Calling this estimate
\begin{equation}
    F_{al}(z) \equiv \ev{\overline{\rho} u_{al,x}u_{al,z}}_x
\end{equation}
we may then measure the agreement of our simulation with analytical expectation
by computing
\begin{equation}
    F(z, t) = \frac{\ev{\rho u_xu_z}_x}.\label{eq:sbm_def}
\end{equation}
Where nonlinear effects are unimportant, we expect $F(z, t) = F_{al}(z)$.
\autoref{fig:lin_fluxes} shows that $F \approx F_{al}$ between $z_0$ and
$z_T$, as expected.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/lin_fluxes.png}
    \caption{$F/F_{al}$ as a function of $z$ at select times $t$. As
    initial transients die out, $F / F_{al} = 1$ to very good agreement above
    the forcing zone $z > z_0 = 2H$ and below the damping zone $z \lesssim z_T =
    9.5H$. The flux excited in the forcing zone is transported without loss to
    the top of the domain, where it is dissipated by the damping layer (see
    \autoref{ss:damping}) without reflection.}\label{fig:lin_fluxes}
\end{figure}

\section{Internal Gravity Waves: Nonlinear Simulation}\label{s:sim}

@@

In \autoref{fig:nl_fluxes}, we plot $\overline{U}$ and $F / F_{al}$ as a function
of $z$ at the times depicted in \autoref{fig:snapshots}. While the behavior of
$\overline{U}$ seems to conform qualitatively with the predictions of
\autoref{ss:crit_layer}, the behavior of $F / F_{al}$ exhibits two notable
features: (i) the incident flux seems to fluctuate greatly with time, and (ii)
there seems to be a small transmitted feature at many of the later times. We
will discuss further these features in \autoref{ss:reflectivity}, after first
analyzing the propagation of the critical layer.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/nl_fluxes.png}
    \caption{Plot of $\overline{U}(z, t)$ and $F(z, t) / F_{al}(z)$ respectively
    at the same times in \autoref{fig:snapshots} over $z$ in our $\mathrm{Re} =
    1024$ simulation. $\overline{U}, F$ follow their definitions in
    \autoref{eq:mean_flow} and \autoref{eq:sbm_def}. $\overline{U}$ is given in
    units of $\overline{U}_c = \frac{\omega}{k_{x}}$ the critical horizontal
    flow velocity (see \autoref{ss:crit_layer}). The propagation of the critical
    layer towards lower $z$ and sharp deposition of $F$ at the critical layer
    are evident.}\label{fig:nl_fluxes}
\end{figure}

@@

For the simulation shown in \autoref{fig:nl_fluxes}, we may analyze the location
of the critical layer. As the simulations are very noisy, we measure the location
of the critical layer using an average of where flux deposition occurs
\begin{align}
    z_{c, \min} &= \argmin_z \z{z: F(z) < 0.3F_{al}},\nonumber\\
    z_{c, \max} &= \argmax_z \z{z: F(z) > 0.3F_{al}},\nonumber\\
    z_c &\equiv \frac{z_{c, \min} + z_{c, \max}}{2}.\label{eq:zc_def}
\end{align}
This was found to a relatively stable estimator of the critical layer location.
Other estimators were used and do not significantly change the results of the
analysis.

The evolution of $z_c$ depends on the deposited flux $\Delta F(t)$ per
\autoref{eq:zc_anal}. To estimate $\Delta F(t)$ across the critical layer $z_c$
from the data, we defined:
\begin{align}
    F_{<}(t) &= \ev{F(z)}_{z \in [z_c - \Delta z - H, z_c - \Delta z]}
        ,\label{eq:sbelow_def}\\
    F_>(t) &= \ev{\z{F(z): F(z) < 0}}_{z \in [z_c, z_c + \Delta z]},
        \label{eq:sabove_def},\\
    \Delta F(t) &\equiv F_>(t) - F_{<}(t).\label{eq:ds_def}
\end{align}
$\ev{\dots}_{z \in [z_a, z_b]}$ denotes averaging over interval $[z_a, z_b]$.
Below the critical layer, we average over an interval of length
$\frac{2\pi}{k_{z}}$ a full vertical wavelength. The offset $\Delta z$ is
necessary to make a measurement of the incident flux unaffected by the
turbulence within the critical layer itself. The height of the critical layer is
limited by $\mathrm{Ri} \lesssim 1$, which bounds its vertical extent $\sim
\frac{1}{k_{z}}$. We empirically found an offset of $\Delta z = \frac{3}{k_z}$
was necessary to be sufficiently far from strong fluctuations near the critical
layer.

Above the critical layer, waves decay over a much smaller vertical extent as
they have larger $z$ wavenumbers thanks to the shear flow Doppler shift.
Accurate measurement of these fluctuations above the critical layer is important
to measuring the transmission feature accurately, seen in
\autoref{fig:nl_fluxes} to be weak and attenuate quickly.

@@

To measure the reflected horizontal momentum flux, we recall from our linear
simulations described in \autoref{ss:lin_ns} that we are able to accurately
predict the incident flux from the incident wave amplitude. Thus, we write for
incident flux
\begin{equation}
    F_i(t) \equiv \ev{\rho u_{x} u_{z}}_x\hat{A}_i^2(t).
\end{equation}
But then, since we already have $\Delta F(t), F_>(t)$ jump and transmitted flux
across the critical layer at time $t$ respectively, we can immediately write
down the reflected flux
\begin{equation}
    F_r(t) = F_i(t) + \Delta F(t) - F_>(t).
\end{equation}
Note that $F_>(t)$ is just the transmitted flux across the critical layer, since
there is no other flux above the critical layer. We then define flux
reflectivity and transmissivity coefficients
\begin{align}
    \mathcal{R}_F(t) &\equiv -\frac{\ev{F_r}(t)}{\ev{F_i}(t)},&
    \mathcal{T}_F(t) &\equiv -\frac{\ev{F_>}(t)}{\ev{F_i}(t)}.
        \label{eq:srefl_def}
\end{align}

@@

Finally, we consider the impact of magnetic winding. In \citep{bukart}, magnetic
winding is used to enforce solid body rotation on the grounds that $t_A \gg
t_{gw}$, where
\begin{equation}
    t_A = \int\limits_0^R \frac{\sqrt{4\pi \rho}}{B_0}\;\mathrm{d}r
        \sim 10^2\;\mathrm{yr}\p{\frac{10^3\;\mathrm{G}}{B}}.
\end{equation}
the Alfv\'en wave crossing time (evaluated for a CO WD in \citealt{fullerIV})
measures the magnetic coupling time and $t_{gw}$ measures the gravitational wave
inspiral timescale. Before solid body rotation is attained, another relevant
timescale is the synchronization timescale $t_s$. For a tidal torque $\tau$ and
tidal forcing frequency $\sigma = m\p{\Omega - \Omega_{spin}}$, we note that
angular momentum transfer is $\pd{M_{sync}}{t} \sigma R^2 = \tau$, where
$M_{sync}$ denotes the mass of the WD that has synchronized. Thus, the
synchronization timescale is
\begin{align}
    t_{sync} &\sim \frac{M_{sync}\sigma R^2}{\tau},\nonumber\\
        &\sim 2 \times 10^5\;\mathrm{yr}
            \p{\frac{M}{M_{\odot}}}
            \p{\frac{\sigma}{2\pi / (1\;\mathrm{hr})}}
            \p{\frac{R}{R_{\oplus}}}^2
            \p{\frac{10^{-14} GM_{\odot}^2/R_{\oplus}}{\tau}}.
\end{align}
A representative $\tau$ has been taken from \citep{bukart}. However, since only
the outer $\sim 10^{-4}M_{\odot}$ need be heated for the thermodynamically
interesting effects studied in \citep{fullerIV} and \citep{tidal_novae}, it
seems that magnetic winding cannot absolutely rule out energetic outbursts such
as tidal novae resulting from strong shear flows.

>>>>

% cp ../sims/agg.png plots; cp ../sims/2d_4_fourier/snapshots_lin_0_masked/f_amps.png plots/lin_amps.png; cp ../sims/2d_4_fourier/snapshots_lin_0_masked/fluxes.png plots/lin_fluxes.png; cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_amps.png plots/nl_f_amps.png; cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/fluxes.png plots/nl_fluxes.png; cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_refl.png plots/nl_f_refl.png; cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_ri.png plots/nl_f_ri.png; cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/front.png plots/nl_front.png;

@@

% An equivalent estimate given by \citep{eliassen_palm_cite,sutherland0} is that
% IGWs break when the wave-induced mean flow is equal to the horizontal phase
% velocity
% \begin{equation}
%     \overline{U}(z) = \frac{\ev{u_{x}u_{z}}_x}{c_{g,z}} \sim
%         \frac{\omega}{k_x},\label{eq:rip}
% \end{equation}
% where \overline{U}(z) \equiv \ev{u_x}_x$ is the mean flow of the fluid.
% \autoref{eq:rip} provides a leading-order estimate for \overline{U}(z)$ which
% may further evolve over time (see \autoref{ss:crit_layer}); for a general mean
% flow, \autoref{eq:rip} also defines the criterion for a \emph{critical
% layer}. This wave-induced mean flow is analogous to Stokes' drift for surface
% waves and can be derived by considering the propagation of $F$
% (\autoref{eq:F_def}) into a medium at rest. Evaluating \autoref{eq:rip}
% yields agreement with \autoref{eq:nl}.

\citealt{drazin, klostermeyer, winters1994} describe the onset of wave breaking.
At intermediate amplitudes, wave breaking occurs via triadic resonances which
transfer energy from the ``parent’’ internal gravity wave (in our problem, the
tidally forced wave) to ``daughter’’ internal gravity waves on smaller length
scales that efficiently damp. The horizontal momentum flux decreases from $F$ to
$0$ over this breaking region. The lost flux is deposited into mean flow
\begin{equation}
    \overline{U}(z, t) \equiv \ev*{u_x}_x.\label{eq:mean_flow}
\end{equation}
As the mean flow grows, a \emph{critical layer} may form, discussed below.

\subsection{Critical Layers}\label{ss:crit_layer}

% TODO stash here
\begin{equation}
    \overline{U}_c \equiv \omega/k_x,
\end{equation}
The further evolution of the critical layer with the incident IGW is
thought to be responsible for tidal synchronization in stellar binaries
\citep{zahn75,gn89} as well as terrestrial phenomena such as the quasi-biennial
oscillation \citep{lindzen_qbo}.

@@

Consider the horizontal momentum transfer at the critical layer. Any incident
horizontal momentum flux absorbed by the fluid must manifest as additional
horizontal momentum of the shear flow. Since $\overline{U}$ cannot exceed
$\overline{U}_c$, the critical layer will instead propagate downward in response
to the incident momentum flux. The horizontal momentum of the shear flow
satisfies
\begin{equation}
    \pd{}{t}\int\limits \overline{\rho}(z) \overline{U}(z, t)\;\mathrm{d}z
        - \Delta F = 0,
\end{equation}
where $\Delta F > 0$ is the absorbed horizontal momentum. Assuming
$\overline{U}(z > z_c) = \overline{U}_c, \overline{U}(z < z_c) = 0$, this
condition becomes
\begin{equation}
    \overline{\rho}(z_c) \overline{U}_c\rd{z_c}{t} = \Delta F.\label{eq:zc_anal}
\end{equation}
If $\Delta F$ is constant in time, $z_c(t)$ has analytical solution
\begin{equation}
    z_c(t) = -H\ln \s{e^{-\frac{z_c(t = 0)}{H}} +
        \frac{t\Delta F}{\overline{U}_c H\overline{\rho}_0}},\label{eq:zc_sol}
\end{equation}
where $z_c(t = 0)$ is the initial critical layer height.

\section{Numerical Simulation Setup}\label{ss:numerics}

@@

\subsection{Parameter Choices}

@@

    \item $C$: In our weak forcing simulations, we first choose $C$ forcing
        strength such that $\xi_z k_z \ll 1$ is satisfied everywhere in the
        simulation domain. This constrains $C$ by \autoref{eq:uz_lin}.

@@

We aim to damp waves that reach the edge of the simulation domain without
inducing nonphysical reflection. To do so, we replace material derivatives
in \autoref{se:nl_upsilon} with:
\begin{align}
    \md{}{t} &\to \md{}{t} + \Gamma(z)\Upsilon,\nonumber\\
    \Gamma(z) &= \frac{1}{2\tau}\s{2 + \tanh \frac{z - z_T}{\Delta z}
        + \tanh \frac{z_B - z}{\Delta z}},\label{eq:Gamma}
\end{align}
where $z_B = 1.5H, z_T = 10.5H$ are the boundaries of the damping zone.
This strongly damps perturbations below $z_B$ and above $z_T$ with damping time
$\tau$, negligibly affects dynamics between $z_B, z_T$ and has transition width
governed by $\Delta z$. We use $\Delta z = 0.25H$ and $\tau = 1/15N$. This
prescription is similar to \citep{lecoanet_damp} and has the advantage of being
smooth, important for spectral methods. Further details of our implementation of
the fluid equations in Dedalus are described in Appendix~\ref{se:strat_impl}.

\section{Weakly Forced Numerical Simulation}\label{s:weak_sim}

@@

The analytical theory also predicts that the horizontal momentmum flux $F(z, t)$
should be independent of $z$ between the forcing zone where it is generated and
the damping zone where it is dissipated (\autoref{eq:F_def}). We make may a
slightly more accurate estimate of the flux carried in the IGW by directly
substituting $\bm{u}_{al}$ into \autoref{eq:F_def}. Calling this estimate
\begin{equation}
    F_{al}(z) \equiv \ev{\overline{\rho} u_{al,x}u_{al,z}}_x
\end{equation}
we may then measure the agreement of our simulation with analytical expectation
by computing $F$ from the simulation via \autoref{eq:F_def}. Where nonlinear
effects are unimportant, we expect $F(z, t) = F_{al}(z)$.
\autoref{fig:lin_fluxes} shows that $F \approx F_{al}$ between $z_0$ and $z_T$,
as expected.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/lin_fluxes.png}
    \caption{$F/F_{al}$ as a function of $z$ at select times $t$. As
    initial transients die out, $F / F_{al} = 1$ to very good agreement above
    the forcing zone $z > z_0 = 2H$ and below the damping zone $z \lesssim z_T =
    9.5H$. The flux excited in the forcing zone is transported without loss to
    the top of the domain, where it is dissipated by the damping layer (see
    \autoref{ss:damping}) without reflection.}\label{fig:lin_fluxes}
\end{figure}

\section{Wave Breaking Simulations}\label{s:sim}

@@

In \autoref{fig:nl_fluxes}, we plot $\overline{U}$ and $F / F_{al}$ as a function
of $z$ at the times depicted in \autoref{fig:snapshots}. While the behavior of
$\overline{U}$ seems to conform qualitatively with the predictions of
\autoref{ss:crit_layer}, the behavior of $F / F_{al}$ exhibits two notable
features: (i) the incident flux seems to fluctuate greatly with time, and (ii)
there seems to be a small transmitted feature at many of the later times. We
will discuss further these features in \autoref{ss:reflectivity}, after first
analyzing the propagation of the critical layer.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/nl_fluxes.png}
    \caption{Plot of $\overline{U}(z, t)$ and $F(z, t) / F_{al}(z)$ respectively
    at the same times in \autoref{fig:snapshots} over $z$ in our $\mathrm{Re} =
    1024$ simulation. $\overline{U}, F$ follow their definitions in
    \autoref{eq:mean_flow} and \autoref{eq:F_def}. $\overline{U}$ is given in
    units of $\overline{U}_c = \frac{\omega}{k_{x}}$ the critical horizontal
    flow velocity (see \autoref{ss:crit_layer}). The propagation of the critical
    layer towards lower $z$ and sharp deposition of $F$ at the critical layer
    are evident.}\label{fig:nl_fluxes}
\end{figure}

@@

For the simulation shown in \autoref{fig:nl_fluxes}, we may analyze the location
of the critical layer. As $F$ fluctuates significantly in the simulation, we
measure the location of the critical layer using an average of where flux
deposition occurs
\begin{align}
    z_{c, \min} &= \argmin_z \z{z: F(z) > 0.3F_{al}},\nonumber\\
    z_{c, \max} &= \argmax_z \z{z: F(z) < 0.3F_{al}},\nonumber\\
    z_c &\equiv \frac{z_{c, \min} + z_{c, \max}}{2}.\label{eq:zc_def}
\end{align}
This was found to a relatively stable estimator of the critical layer location.
Using other estimators does not significantly change the results of the
analysis.

The evolution of $z_c$ depends on the deposited flux $\Delta F(t)$ per
\autoref{eq:zc_anal}. To measure $\Delta F(t)$ across the critical layer $z_c$
from the data, we defined:
\begin{align}
    F_{<}(t) &= \ev{F(z)}_{z \in [z_c - \Delta z - H, z_c - \Delta z]}
        ,\label{eq:sbelow_def}\\
    F_>(t) &= \ev{\z{F(z): F(z) < 0}}_{z \in [z_c, z_c + \Delta z]},
        \label{eq:sabove_def}\\
    \Delta F(t) &\equiv F_<(t) - F_{>}(t).\label{eq:ds_def}
\end{align}
$\ev{\dots}_{z \in [z_a, z_b]}$ denotes averaging over interval $[z_a, z_b]$.
Below the critical layer, we average over an interval of length
$\frac{2\pi}{k_{z}}$ a full vertical wavelength. The offset $\Delta z$ is
necessary to make a measurement of the incident flux unaffected by the
turbulence within the critical layer itself. The height of the critical layer is
limited by $\mathrm{Ri} \lesssim 1$, which bounds its vertical extent $\sim
\frac{1}{k_{z}}$. We empirically found an offset of $\Delta z = \frac{3}{k_z}$
was necessary to be sufficiently far from strong fluctuations near the critical
layer.

Above the critical layer, waves decay over a much smaller vertical extent as
they have larger $z$ wavenumbers thanks to the shear flow Doppler shift.
Accurate measurement of these fluctuations above the critical layer is important
to measuring the transmission feature accurately, seen in
\autoref{fig:nl_fluxes} to be weak and attenuate quickly. We average only where
$F < 0$ since the decay scale of the trasmitted flux varies in time (see
\autoref{fig:nl_fluxes} again), so this was found to be an adequate way of
measuring only the transmitted flux.

@@

To measure the reflected horizontal momentum flux, we recall from our linear
simulations described in \autoref{s:weak_sim} that we are able to accurately
predict the incident flux from the incident wave amplitude. Thus, we write for
incident flux
\begin{equation}
    F_i(t) \equiv \ev{\rho u_{x} u_{z}}_x\hat{A}_i^2(t).
\end{equation}
But then, since we already have $\Delta F(t), F_>(t)$ jump and transmitted flux
across the critical layer at time $t$ respectively, we can immediately write
down the reflected flux
\begin{equation}
    F_r(t) = F_i(t) - \Delta F(t) - F_>(t).
\end{equation}
Note that $F_>(t)$ is just the transmitted flux across the critical layer, since
there is no other flux above the critical layer. We then define flux
reflectivity and transmissivity coefficients
\begin{align}
    \mathcal{R}_F(t) &\equiv -\frac{\ev{F_r}(t)}{\ev{F_i}(t)},&
    \mathcal{T}_F(t) &\equiv -\frac{\ev{F_>}(t)}{\ev{F_i}(t)}.
        \label{eq:srefl_def}
\end{align}

@@

Finally, we consider the impact of magnetic winding. In \citep{bukart}, magnetic
winding is used to enforce solid body rotation on the grounds that $t_A \gg
t_{gw}$, where
\begin{equation}
    t_A = \int\limits_0^R \frac{\sqrt{4\pi \rho}}{B_0}\;\mathrm{d}r
        \sim 10^2\;\mathrm{yr}\p{\frac{10^3\;\mathrm{G}}{B}}.
\end{equation}
the Alfv\'en wave crossing time (evaluated for a CO WD in \citealp{fullerIV})
measures the magnetic coupling time and $t_{gw}$ measures the gravitational wave
inspiral timescale. Before solid body rotation is attained, another relevant
timescale is the synchronization timescale $t_s$. For a tidal torque $\tau$ and
tidal forcing frequency $\sigma = m\p{\Omega - \Omega_{spin}}$, we note that
angular momentum transfer is $\pd{M_{sync}}{t} \sigma R^2 = \tau$, where
$M_{sync}$ denotes the mass of the WD that has synchronized. Thus, the
synchronization timescale is
\begin{align}
    t_{sync} &\sim \frac{M_{sync}\sigma R^2}{\tau},\nonumber\\
        &\sim 2 \times 10^5\;\mathrm{yr}
            \p{\frac{M}{M_{\odot}}}
            \p{\frac{\sigma}{2\pi / (1\;\mathrm{hr})}}
            \p{\frac{R}{R_{\oplus}}}^2
            \p{\frac{10^{-14} GM_{\odot}^2/R_{\oplus}}{\tau}}.
\end{align}
A representative $\tau$ has been taken from \citep{bukart}. However, since only
the outer $\sim 10^{-4}M_{\odot}$ need be heated for the thermodynamically
interesting effects studied in \citep{fullerIV} and \citep{tidal_novae}, it
seems that magnetic winding cannot absolutely rule out energetic outbursts such
as tidal novae resulting from strong shear flows.
